From OpenACC to OpenMP 4: \\ Toward Automatic Translation

### 2016-04-29 paper.tex
Renamed to paper.tex
Abstract

\maketitle
\begin{abstract}

\end{abstract}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
%\appendix
\end{document}

>>>>

\maketitle
\begin{abstract}
For the past few years, OpenACC has been the primary directive-based API for
programming accelerator devices like GPUs.  OpenMP~4.0 is now a competitor in
this space, with support from different vendors.  In this paper, we describe an
algorithm to convert (a subset of) OpenACC to OpenMP~4; we implemented this
algorithm in a prototype tool and evaluated it by translating the EPCC Level~1
OpenACC benchmarks.  We discuss some of the challenges in the conversion
process and propose what parts of the process should be automated, what should
be done manually by the programmer, and what future research and development is
necessary in this area.
\end{abstract}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
%\appendix
\end{document}
